Gap formation and stability in non-isothermal protoplanetary discs

### 2014-09-19 paper/results.tex
edited linear discussion

\section{Growth of non-axisymmetric modes without the influence of the
  planet}
%We first consider the linear stability of planetary gaps.  
In this section, the planet is introduced at $t=20P_0$ and 
its potential switched on over $10P_0$. At $t=30P_0$ we switch off the
planet potential and azimuthally average the surface density, energy
and velocity fields. At this point the planet has carved a partial
gap. We then perturb the density field and continue to 
evolve the disc. This procedure allows us to analyse the growth of
non-axisymmetric modes associated with the gap, but without
complications from non-axisymmetry arising directly from disk-planet
interaction.

Simulations were resolved with grid divisions of $(N_r,N_{\phi})=(1024,2048)$ with $r_{\mathrm{out}}=25r_{\mathrm{in}}$ for time up to $200P_0$ allowing high resolution and detection of high $m$ structures. Cases of $\tilde{\beta}=0.1,1.0,10.0$ were analyzed to provide a range of fast, moderate, and slowly cooled disks.

%The goal of these simulations is to compliment the disk-planet
%simluations presented later. 
These `planet-off' simulations are not linear stability calculations
since the cooling term in our energy equation restores the initial temperature profile corresponding to $H/r=0.05$, rather than the heated gap edge. Linear stability calculations and adiabatic cases will be further discussed in section~\ref{adiabatic_section}.

%disk-planet leads to heating 
%tcool tries to return it to the initial smooth profile (axisymmetric)
%if tcool > trwi -> temp returns to original value. heated gap not
%captured

%There are two competing effects. Increasing
%$t_\mathrm{cool}$ leads to more heating and hence a larger sound-speed
%$c_s$, which favours instability \citep{li00} since the vortex
%instability is pressre-driven. However, gap-opening requires $r_h>H$,
%so increasing the sound-speed, and hence $H$, leads to a shallower
%gap (see below) and expected to be more stable.

%tcool -> return to initial, t=0 temp. profile
%whereas the `basic state' is the gap profile with structured temp profile

%more details on perturbation: m=1 to 10, amplitude?  
%resolution?

\subsection{Gap structure}
%{\bf plots of the gap structure before instability sets in, e.g. at
%  t=30. surface density perturbation, gen. vortensity perturbation,
%  aspect-ratio. compare diff. beta. gaps become more shallow with
%  increasing cooling time (but not significantly - not enough time for
%  full gap formation). generalized vortensity: extrema smoothed out
%  with increasing cooling - expect more stability. aspect-ratio:
%  significant heating. increase in H so expect larger vortices
%}

Since stability of the gap is of interest we analyze the intial state formed by the planet-disk interactions. The intial gap profiles after the averaging procedure are shown in Fig \ref{intial1D} for varying $\tilde\beta$. Gaps formed are shallower for lower $\tilde\beta$ (faster cooling) but never significant enough to form a clear gap in this short timeperiod. Quicker cooling rates also result in steeper density gradients at the gap boundry and both the density maxima and density minima correspondingly increase and decrease with lower $\tilde\beta$. For all cases the gap width is $\approx 5r_{hill}$ which is set by torque balances in the disk \citep{crida06}.

 Generalized vortensity profiles show smoothening with larger cooling rates with the extrema becoming less pronounced. Charactereristicly for such disk-planet Rossby vortices the generalized vortensity minima correspond to density maxima in the disk. Larger $\tilde\beta$ values also as expected result in higher disk aspect ratios $H/r$, which is a value directly correlated to temperature in our model.

 For a planet to carve a gap in the surrounding material it has been shown that $q>H^3$ is needed \citep{crida06}. This indicates that for hotter disks, which have respectively higher $H$, it becomes more difficult by a cubic dependence for planet induced gaps to be formed. This is seen in our simulations as changes in $\tilde{\beta}$ result in changes of $h$ by less than $20\%$ yet gap depth almost doubles. Since generalized vortensity extrema are also correspondingly less pronounced and density gradients become smaller we expect that the stability of gaps to increase with larger $\tilde{\beta}$.

\begin{figure}
  \includegraphics[width=.4\textwidth,clip=true,trim=0.5cm
    2cm 0cm 0cm]{figures/compare_sigma}
  \includegraphics[width=.4\textwidth,clip=true,trim=0.5cm
    2cm 0cm 1cm]{figures/compare_gvortensity}
\includegraphics[width=.4\textwidth,clip=true,trim=0.5cm
    0.5cm 0cm 1cm]{figures/compare_aspectratio}
  \caption{Gap profiles at $t=30P_0$ for the intial partial gap opened before instability emerges for quick (solid line), moderate (dashed line), and slow cooling (broken line). Relative density pertibation (top), generalized vortensity pertibation (middle) and disk aspect ratio (bottom) are shown. \label{intial1D}}
\end{figure}

@@

\begin{table}
  \centering
  \caption{Dominant mode and growth rates for $\tilde{\beta}=0.1,1.0,10.0$ (fast, moderate, and slow cooling) values during `planet-off' simulations \label{modetable}}
  \hfill
  \begin{minipage}{0.3\linewidth}
    \begin{tabularx}{\textwidth}{l R} 
      \multicolumn{2}{c}{$\tilde{\beta}=0.1$} \\ 
      \toprule
      m & $\gamma10^2/\Omega(r_p)$ \\
      \midrule
      6 & 7.3 \\
      7 & 7.8 \\
      8 & 7.9 \\
      9 & 7.9 \\
      10 & 6.8 \\ 
      \bottomrule
    \end{tabularx}
  \end{minipage}
  \hfill
  \begin{minipage}{0.3\linewidth}
    \begin{tabularx}{\textwidth}{l R} 
      \multicolumn{2}{c}{$\tilde{\beta}=1.0$} \\ 
      \toprule
      m & $\gamma10^2/\Omega(r_p)$ \\
      \midrule
      3 & 2.0 \\
      4 & 2.2 \\
      5 & 2.3 \\
      6 & 1.6 \\
      7 & 1.1 \\ 
      \bottomrule
    \end{tabularx}
  \end{minipage}
  \hfill
  \begin{minipage}{0.3\linewidth}
    \begin{tabularx}{\textwidth}{l R} 
      \multicolumn{2}{c}{$\tilde{\beta}=10.0$} \\ 
      \toprule
      m & $\gamma10^2/\Omega(r_p)$ \\
      \midrule
      1 & 1.1 \\
      2 & 1.6 \\
      3 & 1.7 \\
      4 & 1.2 \\
      5 & 0.1 \\ 
      \bottomrule
    \end{tabularx}
  \end{minipage}
  \hfill
\end{table}

\subsection{Linear modes and growth rates}\label{linear}
%{\bf present `planet-off' simulations. one `fourier mode v.s. time'
%  plot to show growth of linear instability. do an adiabatic case (or
%  extremely long cooling time) to see the effect of heated gap edge
%  (i.e. temp doesn't go back to t=0 value too quickly)
%  compare growth rate and dominant
%  m as function of beta (table). 2D figs to contrast (also used to
%  show it's the minimum in generalized pv that goes unstable.    
%  result: increasing cooling time makes the gap
%  more stable, and favors lower m. note: the `basic state' should be
%  the system at t=30 after azimuthal average. linear results should
%  have small perturbations. 
%}
After the azimuthal averaging, the small pertibation excites rapidly growing instabilities by the RWI. We analyticly charcterize these modes with quantities $m$ and $\gamma$ as defined by Eq.~\ref{fouriertransform} and Eq.~\ref{growth}. Table \ref{modetable} contains the results of the mode growth rates for a variety of cooling rates during this semi-linear phase. Results indicate that as $\tilde{\beta}$ was increased from $ 0.1\rightarrow10.0$ the dominant azimuthal Fourier mode decreased from $ m=9\rightarrow3$ and the respective growth rate decreased from $ \gamma/\Omega(r_p)=0.079 \rightarrow 0.017$. Snapshots of the instability in $r-\phi$ plane for the different $\tilde\beta$ are shown in Fig \ref{2Dlinear}.

These `planet-off' simulations, which are reminiscient of linear stability measurements, show that stability of gap edges increase with longer cooling rates (ie hotter gaps). This is as expected from the intial gap profiles and the gap forming criteria discussed in the previous section.

\begin{figure}
  \includegraphics[width=\linewidth,clip=true,trim=1.2cm
    0cm 0cm 0cm]{figures/linear_stability}
  \caption{Log plot of the azimuthal Fourier modes of disk surface density non-dimenionlized by the background mode during the `planet-off' simulations for $\tilde{\beta}=10$. Colors correspond to different $m$ values. The $m=3$ component of the fourier transform is the fast growing mode during this growth phase of the instability and has corresponding $\gamma=0.017\Omega(r_p)$. \label{linearmodes}}
\end{figure}

\begin{figure*}
  \centering
  \subfigure{
    \includegraphics[width=0.3\linewidth]{figures/analysis_gvortensity_lowb}
  }
\hfill
  \subfigure{
    \includegraphics[width=0.3\linewidth]{figures/analysis_gvortensity_medb}
  }
\hfill
  \subfigure{
    \includegraphics[width=0.3\linewidth]{figures/analysis_gvortensity_highb}
  }  
  \caption{Radial plots of the generalized vortensity pertibation for cases of $\tilde{\beta}=0.1,1.0,10.0$ (left,middle,right) during the linear phases of growth. The number of visible vortices decrease as $\tilde{\beta}$ increases and snapshot times correspondingly increase to capture the longer growth phases of the instabilities. \label{2Dlinear}}
\end{figure*}

\subsubsection{Nearly adiabatic disks}
\label{adiabatic_section}
%{\bf a case with extrmely long cooling time (or adiabatic run) in
%  order to look at effect of heated gap edge.  prelim result: not
%  important, at t=30, gap edge only heats to $H/r\simeq0.06$ even for
%  purely adiabatic disk. change in $h$ not important for linear
%  perturbations (but important for setting up the basic state). 
%}
During the `planet-off' simulations the analysis is not truly a linear stability measurement as we do not capture the effects of a heated disk on the instability growth. Since $t_{\mathrm{cool}}<t_{\mathrm{instability}}$ the disk manages to cool back to its intial value of $h=0.05$ before the instability emerges and thus we do not have a steady background state to form a linear stability problem. To compare our 'planet-off' analysis with a true linear stability analysis we ran a simulation  with $\tilde{\beta}=100.0$ which corresponds with an almost adiabtaic case. In this simulation the cooling rate is slow enough that the gap temperature profile changes only marginally over the timescale of the growth of the instability. The results show that the linear stability of the $\tilde{\beta}=100.0$ cases almost exactly equivilant to the case of $\tilde{\beta}=10.0$ in terms of mode growth rates and gap profiles. Since the disk heats up only to values $h\simeq0.06$ in the adiabatic case, the difference in growth rates between this and the original disk temperature of $h=0.05$ changes almost insignificantly as shown by linear theory \citep{li00}. This indicate that a continuously hot gap edge is not as important for development of vortices as the heating effects on the formation of the intial gap state.

%% We first describe results for weakly self-gravitating
%% discs $Q_0=8$ (giving $M_d=0.015M_*$) so that the gap remains 
%% gravitationally stable \citep{lin11b}. We also impose a dimensionless
%% kinematic viscosity $\hat{\nu}=2\times10^{-5}$ to suppress the Rossby
%% vortex instablity \citep{valborro07}. These parameter values
%% are typical for disc-planet simulations and yield stable/steady 
%% gap profiles. This will be useful reference cases to  
%% understand the unstable cases considered later.

%% Fig. \ref{lvisc_steady_gap} shows the steady state gap profiles in terms of the relative
%% surface density and aspect-ratio at $t=200P_0$. Three levels of cooling are considered:
%% $\tbeta=0.1,\,1.0$ and $10.0$ (i.e. $t_c\Omega_k\simeq2.4,\,24$ and $240$). We refer to them as
%% fast, moderate and slow cooling cases, respectively.

>>>>

\section{Growth of non-axisymmetric modes without the influence of the
  planet}
In this section, the planet is introduced at $t=20P_0$ and 
its potential switched on over $10P_0$. At $t=30P_0$ we switch off the
planet potential and azimuthally average the surface density, energy
and velocity fields. At this point the planet has carved a partial
gap. We then perturb the surface density for $r>r_p$ and continue to 
evolve the disc. We impose  sinusoidal perturbations with 
azimuthal wavenumbers $m\in[1,10]$. {\bf what are PERTMIN and PERTMAX values?}  
This procedure allows us to analyse the growth of 
non-axisymmetric modes associated with the gap, but without
complications from non-axisymmetry arising directly from disc-planet
interaction.

Note that these `planet-off' simulations are not linear stability
calculations because since the cooling term in our energy equation
restores the initial temperature profile corresponding to $H/r=0.05$,
rather than the heated gap edge. Linear stability calculations and
adiabatic cases will be further discussed in
section~\ref{adiabatic_section}.

Simulations here employ a resolution of $(N_r,N_{\phi})=(1024,2048)$
and we consider 
%for a time up to $200P_0$ allowing high resolution and detection of high
%$m$ structures.
cases of $\tilde{\beta}=0.1,1,10$ corresponding to fast, moderate,
and slowly cooled discs.

\subsection{Gap structure}
%Since stability of the gap is of interest 
We first examine the gap structure formed by planet-disc
interaction as a function of the cooling time. The azimuthally-averaged 
gap profiles are shown in Fig. \ref{intial1D} for varying
$\tilde\beta$. Gaps formed with lower $\tilde\beta$ (faster cooling)
are deeper with steeper gradients at the gap edges. Faster cooling rates also 
increase and decrease the surface density maxima and 
minima increase, respectively. However, a clean gap does not form
in this short time period.

%For all cases the gap width is $\approx 5r_{hill}$
%which is set by torque balances in the disk \citep{crida06}.

Larger $\tilde\beta$ values result in higher disc aspect ratios $h=H/r$,
i.e. higher temperatures. Heating mostly occur at the gap edges
due to planet-induced spiral shocks. Decreasing the cooling time
implies that this heat is retained in the disc. In the inviscid limit the gap
opening condition is $r_h\gtrsim H$ or $q\gtrsim 3h^3$
\citep{crida06}. 
% which is a value directly correlated to temperature in our model. 
%For a planet to carve a gap in the surrounding material it has been
%shown that $q>H^3$ is needed \citep{crida06}. 
This indicates that for hotter discs (higher
$h$), it becomes more difficult for a planet of fixed $q$ to open a
gap. This explains the shallower gaps in surface density when
$\tilde{\beta}$ is increased.

%This is seen in our simulations as changes in $\tilde{\beta}$
%result in changes of $h$ by less than $20\%$ yet gap depth almost
%doubles.

The important consequence of a heated gap edge is that the
generalized vortensity profiles become smoother with increasing
cooling times, with the extrema becoming less pronounced. Previous locally
isothermal disc-planet simulations show the RWI associated with PV
minima \citep{li05,lin10}. We can therefore expect the RWI to be associated with
minima in the generalized vortensity (corresponding to local surface
density maxima) in the non-isothermal case. Because the extrema are
less sharp, the RWI is expected to be weaker and the gap to be more
stable with longer cooling times.

%Charactereristicly
%for such disk-planet Rossby vortices the generalized vortensity
%minima correspond to density maxima in the disk. 
%Since generalized vortensity extrema are also
% correspondingly less pronounced and density gradients become smaller
% we expect that the stability of gaps to increase with larger
% $\tilde{\beta}$.

\begin{figure}
  \includegraphics[width=\linewidth,clip=true,trim=0.5cm
    2cm 0cm 0cm]{figures/compare_sigma}
  \includegraphics[width=\linewidth,clip=true,trim=0.5cm
    2cm 0cm 1cm]{figures/compare_aspectratio}
\includegraphics[width=\linewidth,clip=true,trim=0.5cm
    0.5cm 0cm 1cm]{figures/compare_gvortensity}
  \caption{Gap profiles at $t=30P_0$ for the intial partial gap opened
    before instability emerges for fast (solid), moderate
    (dashed), and slow cooling (dashed-dot). The relative surface density
    pertibation (top), disc aspectratio (middle) and generalized
    vortensity pertibation (bottom) are shown. \label{intial1D}}  
\end{figure}

@@

\begin{table}
  \centering
  \caption{Dominant mode and growth rates for
    $\tilde{\beta}=0.1,1.0,10.0$ (fast, moderate, and slow cooling)
    values during `planet-off' simulations \label{modetable}} 
  \hfill
  \begin{minipage}{0.3\linewidth}
    \begin{tabularx}{\textwidth}{l R} 
      \multicolumn{2}{c}{$\tilde{\beta}=0.1$} \\ 
      \toprule
      $m$ & $10^2\gamma/\Omega(r_p)$ \\
      \midrule
      6 & 7.3 \\
      7 & 7.8 \\
      8 & 7.9 \\
      9 & 7.9 \\
      10 & 6.8 \\ 
      \bottomrule
    \end{tabularx}
  \end{minipage}
  \hfill
  \begin{minipage}{0.3\linewidth}
    \begin{tabularx}{\textwidth}{l R} 
      \multicolumn{2}{c}{$\tilde{\beta}=1.0$} \\ 
      \toprule
      $m$ & $10^2\gamma/\Omega(r_p)$ \\
      \midrule
      3 & 2.0 \\
      4 & 2.2 \\
      5 & 2.3 \\
      6 & 1.6 \\
      7 & 1.1 \\ 
      \bottomrule
    \end{tabularx}
  \end{minipage}
  \hfill
  \begin{minipage}{0.3\linewidth}
    \begin{tabularx}{\textwidth}{l R} 
      \multicolumn{2}{c}{$\tilde{\beta}=10.0$} \\ 
      \toprule
      $m$ & $10^2\gamma/\Omega(r_p)$ \\
      \midrule
      1 & 1.1 \\
      2 & 1.6 \\
      3 & 1.7 \\
      4 & 1.2 \\
      5 & 0.1 \\ 
      \bottomrule
    \end{tabularx}
  \end{minipage}
  \hfill
\end{table}

{\bf
\subsection{Axisymmetric stability}
Check that the gap profiles are stable against axisymmetric
stability. Can use analytical criteria given in section 3.1 of Li et
al (2000, ApJ, 533, 1023). No plot needed, just statements. 
}

\subsection{Non-axisymmetric instability}\label{linear}
%{\bf present `planet-off' simulations. one `fourier mode v.s. time'
%  plot to show growth of linear instability. do an adiabatic case (or
%  extremely long cooling time) to see the effect of heated gap edge
%  (i.e. temp doesn't go back to t=0 value too quickly)
%  compare growth rate and dominant
%  m as function of beta (table). 2D figs to contrast (also used to
%  show it's the minimum in generalized pv that goes unstable.    
%  result: increasing cooling time makes the gap
%  more stable, and favors lower m. note: the `basic state' should be
%  the system at t=30 after azimuthal average. linear results should
%  have small perturbations. 
%}

%After the azimuthal averaging, the small pertibation excites rapidly
%growing instabilities by the RWI.

In all cases we observe growth of non-axisymmetric structures after the
planet potential is switched off and the system subject to random
perturbations. An example is shown in Fig. \ref{linearmodes} for 
$\tilde{\beta}=10$. We charcterize these
modes with an azimuthal wavenumber $m$ and growth rate $\gamma(m)$ as defined by
Eq.~\ref{fouriertransform}---\ref{growth}. Table \ref{modetable}
lists the growth rates for the three cooling
times, measured during linear growth.

\begin{figure}
  \includegraphics[width=\linewidth,clip=true,trim=1.2cm
    0cm 0cm 0cm]{figures/linear_stability}
  \caption{Evolution of azimuthal Fourier modes of disc surface
    density, non-dimenionlized by the axisymmetric mode for the
    `planet-off' simulations with $\tilde{\beta}=10$. Colours correspond
    to different $m$ values. The $m=3$ component is the fastest growing
    mode during linear growth and has a corresponding
    $\gamma=0.017\Omega(r_p)$. {\bf is the $\Sigma_0$ at
      t=0?} \label{linearmodes}}  
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Table \ref{modetable} show that as
$\tilde{\beta}$ was increased from $ 0.1\rightarrow10$ the dominant
azimuthal Fourier mode decreased from $ m=9\rightarrow3$ and the
respective growth rate decreased from $ \gamma/\Omega(r_p)=0.079
\rightarrow 0.017$. However, despite two orders of magnitude increase in the
cooling time, the instability remains dynamical with growth time
$\lesssim 10P_0$. Snapshots of the instability in $r-\phi$ plane for
the different $\tilde\beta$ are shown in Fig \ref{2Dlinear}.

These `planet-off' simulations show that gap edges become more stable with
longer cooling times. This is expected because larger $\tilde{\beta}$
result in hotter gap profiles at $t=30P_0$ with less pronounced
generalized vortensity minima. Stabilization with increased
cooling time is therefore due to a smoother basic state for the
instability, as it is more difficult for the planet to open a gap if
the disc is allowed to heat up.

% which result in hotter gaps since the heating
%due
%This is as expected from the
%intial gap profiles, because 
% and the gap forming criteria discussed in the
%previous section.

\begin{figure*}
  \centering
  \subfigure{
    \includegraphics[width=0.3\linewidth]{figures/analysis_gvortensity_lowb}
  }
\hfill
  \subfigure{
    \includegraphics[width=0.3\linewidth]{figures/analysis_gvortensity_medb}
  }
\hfill
  \subfigure{
    \includegraphics[width=0.3\linewidth]{figures/analysis_gvortensity_highb}
  }  
  \caption{Generalized vortensity perturbation (relative to $t=0$) for
    cases of $\tilde{\beta}=0.1,1,10$ (left,middle,right) during
    the growth of non-axisymmetric modes. The planet potential has
    been switched off.  The number of vortices
    decrease as $\tilde{\beta}$ increases. Note that snapshots are
    taken later because it takes longer for the vortices to grow and
    become visible with increasing cooling time. 
    %    correspondingly increase to capture the longer growth phases of
    %    the instabilities. 
    \label{2Dlinear} {\bf I'm curious to know if plots clearer if
      perturbations are measured relative to t=30? remember t=30 is
      our reference state for instability. But we'll probably keep
      these for consistency (later non-linear plots are all measure
      with respect to t=0).}} 
\end{figure*}

\subsubsection{Nearly adiabatic discs}
\label{adiabatic_section}
%{\bf a case with extrmely long cooling time (or adiabatic run) in
%  order to look at effect of heated gap edge.  prelim result: not
%  important, at t=30, gap edge only heats to $H/r\simeq0.06$ even for
%  purely adiabatic disk. change in $h$ not important for linear
%  perturbations (but important for setting up the basic state). 
%}
The above `planet-off' simulations are not formally linear
stability calculations, because the cooling time is shorter
than the instability growth time, 
%
%as we do not capture the effects of a heated
%disk on the instability growth. 
$t_c<\gamma^{-1}$.  
Thus the disk cools back to its intial value of $h=0.05$
before or during the instability growth, implying we do not have a
steady basic state to formulate a standard linear stability
problem. %This means the disc temperture of $h=0.05$ in the the above cases

In order to perform a proper linear stability analysis and capture the
effect of a heated gap edge during instability growth, we ran a simulation  with
$\tilde{\beta}=100$, corresponding to an almost adiabtaic disc.  
%To compare our 'planet-off' analysis with a true
%linear stability analysis 
In this simulation the cooling rate is slow enough that the gap 
temperature profile (e.g. middle panel of Fig. \ref{intial1D}) changes
only marginally over the instability growth timescale. %heat is
                                %retained/maintained.

We find very similar gap profiles and mode growth rates for
$\tilde{\beta}=100$ as with $\tilde{\beta}=10$. The disc heats up to
values $h\simeq0.06$ in the nearly adiabatic case. This is close to
the original temperature of $h=0.05$, so growth rates are not expected
to change significantly according to the linear theory presented in
\citep{li00}.

According to \cite{li00}, increasing $h$ increases linear growth rates
of the RWI because it is pressure-driven. However, in the case 
of disc-planet interaction, increasing $h$ has a stabilizing effect
through the gap profile because it results in smoother gap
edges. The fact that we observe smaller growth rates as $h$ is
increased indicate that for planetary gaps, the importance of $h$ on
the \emph{linear} RWI is through the setting the gap profile (i.e. basic
state for the instability).

%results in shallower gaps
%which is expected to be

%the difference in growth rates between this and the
%original disc temperature of $h=0.05$ changes almost insignificantly
%as shown by linear theory \citep{li00}. 
%Although linear
%theory predicts higher growth rates with increasing $h$

%This indicate that a
%continuously hot gap edge is not as important for development of
%vortices as the heating effects on the formation of the intial gap
%state.

{\bf
If there's time, repeat planet off simulations but keep the planet on
until $t=40P_0$ or $50P_0$. Look at stability properties when the gaps
are generally deeper (including the nearly adiabatic case). Although
with the planet instability may already appear by $t=40P_0$, the
azimtuhal average performed prior to perturbations will erase it. 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
